---
title: "Video Game Sales Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---
<style type="text/css">

.navbar {  
    background-color: #4682B4;
    border-color: #4682B4;
    font-family: Cambria;
    font-color: white;
}

.navbar-brand {
  font-size: 35px;
}
.sidebar {
   background-color: white;
   font-family: Cambria;
   color: #4682B4;
   ont-color: #4682B4;
   font-size: 25px;
  }

  
.chart-title {  /* chart_title  */
   font-size: 20px;
   font-family: Cambria;
}



</style>
```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(dygraphs)
library(highcharter)
library(DT)
```


```{r data}
file_url <- "https://raw.githubusercontent.com/MdShehabKhan/Dashboard/main/Video%20game%20sales.csv"

game <- read.csv(file = file_url, stringsAsFactors = FALSE) 


yr <- game |> select(Year) |> distinct() |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  mutate(Year=as.numeric(Year)) |>  arrange(Year)

```

Yearly Sales
======================================================================

## Sidebar {.sidebar data-width="350"}

```{r}
sliderInput(inputId = "year",label = "Year", min = 1980, max = 2016, value = yr, ticks = T,animate = F,sep = "",width = 350)
```

## Row {data-height="150"}

### Sale on North America

```{r}


renderValueBox({
    valueBox(caption = tags$p(paste0("Sale in North America - ", input$year), style = "font-size: 120%; 
                              font-family: Cambria; 
                              font-weight: bold;
                              color: #39678E;"),
      tags$object(game |> select(Year, NA_Sales) |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  group_by(Year) |> 
  summarise(na=sum(NA_Sales, na.rm = T)) |>
  mutate(Year=as.numeric(Year)) |>
  arrange(Year) |> 
  filter(Year==input$year) |> 
    pull(na),style = "font-size: 120%; font-family: Cambria; color: #39678E;"), 
      icon = "fa-dollar",
      color = "#A7C7E7"
    )
  })


```

### Chart A2

```{r}


renderValueBox({
    valueBox(caption = tags$p(paste0("Sale in Europe - ", input$year), style = "font-size: 120%; 
                              font-family: Cambria; 
                              font-weight: bold;
                              color: #2A4040;"),
      tags$object(game |> select(Year, EU_Sales) |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  group_by(Year) |> 
  summarise(eu=sum(EU_Sales, na.rm = T)) |> 
  mutate(Year=as.numeric(Year)) |>
  arrange(Year) |> 
  filter(Year==input$year) |> 
    pull(eu),style = "font-size: 120%; font-family: Cambria; color: #2A4040;"), 
      icon = "fa-euro",
      color = "#5F9EA0"
    )
  })

```

### Chart A3

```{r}

renderValueBox({
    valueBox(caption = tags$p(paste0("Sale in Japan - ", input$year), style = "font-size: 120%; 
                              font-family: Cambria; 
                              font-weight: bold;
                              color: #616194 ;"),
      tags$object(game |> select(Year, JP_Sales) |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  group_by(Year) |> 
  summarise(jp=sum(JP_Sales, na.rm = T)) |> 
  mutate(Year=as.numeric(Year)) |>
  arrange(Year) |> 
  filter(Year==input$year) |> 
    pull(jp),style = "font-size: 120%; font-family: Cambria; color: #616194 ;"), 
      icon = "fa-yen",
      color = "#CCCCFF"
    )
  })
```

### Chart A4

```{r}

renderValueBox({
    valueBox(caption = tags$p(paste0("Global Sale - ", input$year), style = "font-size: 120%; 
                              font-family: Cambria; 
                              font-weight: bold;
                              color: #415C57 ;"),
      tags$object(game |> select(Year, JP_Sales) |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  group_by(Year) |> 
  summarise(jp=sum(JP_Sales, na.rm = T)) |> 
  mutate(Year=as.numeric(Year)) |>
  arrange(Year) |> 
  filter(Year==input$year) |> 
    pull(jp),style = "font-size: 120%; font-family: Cambria; color: #415C57 ;"), 
      icon = "fa-globe",
      color = "#96DED1"
    )
  })

```

## Row {data-height="700"}

### Sales Trend

```{r}
na <- 
game |> select(Year, NA_Sales) |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  group_by(Year) |> 
  summarise(na=sum(NA_Sales, na.rm = T)) |>
  mutate(Year=as.numeric(Year)) |>
  arrange(Year)

na <- 
game |> select(Year, NA_Sales) |> 
  filter(Year!="N/A") |> 
  group_by(Year) |> 
  summarise(na=sum(NA_Sales, na.rm = T)) |>
  mutate(Year=as.numeric(Year)) |>
  arrange(Year)


eu <- 
game |> select(Year, EU_Sales) |> 
  filter(Year!="N/A") |> 
  group_by(Year) |> 
  summarise(eu=sum(EU_Sales, na.rm = T)) |> 
  mutate(Year=as.numeric(Year)) |>
  arrange(Year) 


jp <- 
game |> select(Year, JP_Sales) |> 
  filter(Year!="N/A") |> 
  group_by(Year) |> 
  summarise(jp=sum(JP_Sales, na.rm = T)) |> 
  mutate(Year=as.numeric(Year)) |>
  arrange(Year)


glb <- 
game |> select(Year, Global_Sales) |>
  filter(Year!="N/A") |> 
  group_by(Year) |> 
  summarise(glb=sum(Global_Sales, na.rm = T)) |> 
  mutate(Year=as.numeric(Year)) |>
  arrange(Year) 

sales <- 
na |> full_join(eu, by="Year") |>
  full_join(jp, by="Year") |> 
  full_join(glb, by="Year") |> 
  filter(!(Year %in% c("N/A", 2020, 2017))) 

name <- c("Year","NA","EU","JP","GLB")

names(sales) <- name

graph <- 
dygraph(sales) |> dyRangeSelector()

renderDygraph(graph)
```

Genre wise Sales
======================================================================

Row
-------------------------------------
    
### North America
    
```{r}
na_g <- 
game |> select(Genre, NA_Sales) |> 
  group_by(Genre) |> 
  summarise(sale_in_mln=sum(NA_Sales, na.rm = T)) |> 
  arrange(desc(sale_in_mln))

na_g |> 
  hchart(
    "treemap", 
    hcaes(x = Genre, value = sale_in_mln, color=sale_in_mln)
    ) |> hc_colorAxis(minColor = "#F14B4B",
    maxColor = "#3775A1") 
```
 
### Europe
    
```{r}
eu_g <- 
game |> select(Genre, EU_Sales) |> 
  group_by(Genre) |> 
  summarise(sale_in_mln=sum(EU_Sales, na.rm = T)) |> 
  arrange(desc(sale_in_mln))

eu_g |> 
  hchart(
    "treemap", 
    hcaes(x = Genre, value = sale_in_mln, color=sale_in_mln)
    ) |> hc_colorAxis(minColor = "yellow",
    maxColor = "#234BD3")
``` 

Row
-------------------------------------
    
### Japan
    
```{r}
jp_g <- 
game |> select(Genre, JP_Sales) |> 
  group_by(Genre) |> 
  summarise(sale_in_mln=sum(JP_Sales, na.rm = T)) |> 
  arrange(desc(sale_in_mln))

jp_g |> 
  hchart(
    "treemap", 
    hcaes(x = Genre, value = sale_in_mln, color=sale_in_mln)
    ) |> hc_colorAxis(minColor = "white",
    maxColor = "#EA4828")
```
    
### Global

```{r}
glb_g <- 
game |> select(Genre, Global_Sales) |> 
  group_by(Genre) |> 
  summarise(sale_in_mln=sum(Global_Sales, na.rm = T)) |> 
  arrange(desc(sale_in_mln))

glb_g |> 
hchart(
    "treemap", 
    hcaes(x = Genre, value = sale_in_mln, color=sale_in_mln)
    ) |> hc_colorAxis(minColor = "green",
    maxColor = "#713333")
```

Top 10
======================================================================
## Sidebar {.sidebar data-width="350"}

```{r}
sliderInput(inputId = "year2",label = "Year", min = 1980, max = 2016, value = yr, ticks = T,animate = F,sep = "",width = 350)
```


Row
------------------------------------- 
```{r}


renderDataTable(game |> select(Name,Year, Publisher,NA_Sales,EU_Sales, JP_Sales,Global_Sales) |> filter(!(Year %in% c("N/A", 2020, 2017))) |> 
  mutate(Year=as.numeric(Year)) |>
  group_by(Year,Name,Publisher) |> 
  summarise(na=sum(NA_Sales, na.rm = T),
            eu=sum(EU_Sales, na.rm = T),
            jp=sum(JP_Sales, na.rm = T),
            glb=sum(Global_Sales, na.rm = T)) |> 
  mutate(total=na+eu+jp+glb) |> 
  select(Year, Name, total,Publisher) |> 
  filter(Year==input$year2) |>
  arrange(desc(total)) |>
  head(10) |> 
  ungroup() |> 
  mutate(Rank = dense_rank(desc(total))) |> 
  select(Rank,Name,Publisher) |> 
  rename(Game=Name), filter = "none",rownames = F,options = list(pageLength = 10), autoHideNavigation = T)

```

